---
title: 'Engagement Report: Group 2'
author: 'Chenxi Du, Ian Fowler, Natalie Hakim, & Yu Cao'
date: '`r Sys.Date()`'
output:
  html_document:
    highlight: tango
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, read-config, include = FALSE}
WHICH_CONFIG <- Sys.getenv("WHICH_CONFIG")
config_list <- config::get(
  config = WHICH_CONFIG
)
```

```{r here}
here::i_am('engage_report.Rmd')
```

```{r load data}
table1 <- readRDS(
  here::here('output/table1.rds')
)

plot1 <- knitr::include_graphics(
  here::here('output/plot1.png')
)

plot2 <- knitr::include_graphics(
  here::here('output/plot2.png')
)

reg_title_tbl <- readRDS(
  here::here('output/reg_title_tbl.rds')
)

reg_topic_tbl <- readRDS(
  here::here('output/reg_topic_tbl.rds')
)

reg_week_tbl <- readRDS(
  here::here('output/reg_week_tbl.rds')
)
```

## Descriptive Analysis

### Table 1

__Table 1__ describes the characteristics of the overall set of videos _(n = 80)_

```{r table 1}
table1
```

### Plot 1

__Plot 1__ describes the distribution of video statistics

```{r plot 1, echo=FALSE, out.width="50%", fig.cap="Plot1 Distribution of the variables", fig.align = "center", out.width = "700px"}
plot1
```

### Plot 2

__Plot 2__ describes the correlation of the video statistics

```{r plot 2, echo=FALSE, out.width="50%", fig.cap="Plot2 Correlation heatmap of the variables", fig.align = "center", out.width = "700px"}
plot2
```

## Regression Analysis

The __regression table__ below describes the results of the regression of unique viewers by _video title_, _video topic_, or _week of upload_

```{r regression table, title, include=config_list$title}
reg_title_tbl
```

```{r regression table, topic, include=config_list$topic}
reg_topic_tbl
```

```{r regression table, week, include=config_list$week}
reg_week_tbl
```
